Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-09-09 Final_Manuscript.Rmd
edits to participants section and analysis strategy

@@

Data from two different, but demographically equivalent, higher education institutions in the Northeast United States were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study. In the measures section that follows we refer to them as Sample 1 and Sample 2. Thirty-two previously unacquainted self-identifying female-sex dyads (64 total participants) from institutions in the Northeast of the United States participated in this study. Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college. More specifically, twelve of the pairs were students at a co-ed liberal arts college, while the remaining twenty pairs attended a women’s liberal arts college. [Footnote: Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals. Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2. For consistency, we limited participant data to same sex female pairs at the two colleges.]

@@

Due to these similarities across samples in regard to correlation patterns between significant variables within this study, the two datasets were combined. These participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`). The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race. There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs. The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs. `r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.

@@

soo_diff <- t.test(a2pSOO_A ~ (sexor_A == 1), data = clarksmith_women)
```
To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner [@garcia2016objectification]. Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts. All questions were rated on a scale from 1 (not at all) to 7 (constantly). Objectification was measured by getting the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intsoo_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_extsoo_alpha)[1,1]` for Sample 2). A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.

@@

```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
include_graphics("2016_figure.jpg")
```
This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO). See Figure\ \@ref(fig:2016figure) for the results of the analysis from this previous study. We investigated how the central effects found in the previous study relate to interactions between two women. Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction. In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in @garcia2016objectification. Further, we will investigate the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance. [Asha: This section feels like a mixture of explaining what the study was intended to investigate as wel as future directions. Is that the point, or can this be organized better?]

While @garcia2016objectification used dyadic path analysis, the current study used multilevel modeling for our dyadic analyses. Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation]. One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural]. Further, @olsen2006structural detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models. The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation patterns. The online supplementary materials contains analysis using SEM. See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.

Testing the @garcia2016objectification model on the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approach for each outcome variable (i.e., endogenous variable in Figure\ \@ref(fig:2016figure)). Thus, we ran five APIM's to test all the hypothesized relationships. See Figure\ \@ref(fig:apim) for a basic APIM model. The APIM includes effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$). Unlike the original @garcia2016objectification study, our study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary. Recall that the indistinguishable nature of the dyads in the current study led us to choose the MLM approach over SEM. These analyses are considered exploratory, given the lack of prior research theorizing about these linkages.

Before moving to the main analyses, we discuss statistical equivalence tests that provide support for combining Sample 1 and Sample 2 in one analysis sample. The online supplemental material contains the main analyses separated by samples. All results presented below are from models including sample as a control variable.

@@

### Combining Samples
```{r}
##Correlations
round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Smith"), 
                 a2pSOO_A, a2pSOO_P, TSO_A,
                 howbody_avg_A,
                 authenticity_A, 
                 trigram_score_A, careerasp_A, relag_A))$r, 3)

round(corr.test(select(filter(clarksmith_women, smith_or_clark == "Clark"), 
                 a2pSOO_A, a2pSOO_P, TSO_A, 
                 howbody_avg_A,
                 authenticity_A, 
                 trigram_score_A, careerasp_A, relag_A))$r, 3)
```
The correlations between study variables is similar across samples. The reliabilities for the study scales were also equivalent. (Note that the two samples were two small to conduct formal measurement equivalence tests for scales.) There are no statistically significant differences between samples in demographics including age, STATS, and ethnicity, STATS.

>>>>

These hypotheses are considered exploratory, given the lack of prior research theorizing about these linkages.

@@

Data from two demographically equivalent higher education institutions in the Northeast United States were combined to create the final analysis sample (*N =* `r nrow(clarksmith_women)`) used in this study. In the measures section that follows we refer to them as Sample 1 and Sample 2. Thirty-two previously unacquainted self-identifying female dyads (64 total participants) from institutions in the Northeast of the United States participated in this study. Sample 1 (*N =* `r ns[3]`) is from a co-ed liberal arts college and Sample 2 (*N =* `r ns[4]`) is from a women’s liberal arts college. More specifically, twelve of the pairs were students at a co-ed liberal arts college, while the remaining twenty pairs attended a women’s liberal arts college. [Footnote: Initially, data was collected from same-sex and mixed-sex dyads that comprised of male and female gendered individuals. Sample 1 originally consisted of twenty-two pairs, twelve men and thirty-two women. Twenty-three pairs made up of forty-three women and one man, as well as two participants who did not identify with either gender category, formed Sample 2. For consistency, we limited participant data to same sex female pairs at the two colleges.] All results presented below are from models including sample as a control variable.

@@

The participants were mostly first-year college students, with an average age of `r mean_age` (SD = `r sd_age`). The sample was `r percent_white`% White/European American, `r percentage_black`% Black/African-American, `r percent_asian`% Asian/Pacific Islander, `r percent_latinx`% Latinx, and `r percent_other`% mixed-race. There were `r samerace_white` White/White pairs and `r samerace_minority` same race racial minority pairs, for a total of `r samerace_white + samerace_minority` same-race pairs. The remaining `r mixedrace_white + mixedrace_minority` were mixed race pairs, of which `r mixedrace_white` were White/racial minority pairings and `r mixedrace_minority` were cross-racial minority group pairs. `r percent_straight`% of the sample identified as heterosexual, and `r percent_queer`% identified as gay, lesbian or bisexual.

@@

soo_diff <- t.test(a2pSOO_A ~ (sexor_A == 1), data = clarksmith_women)
```
To measure the participant’s objectification of their partner in the interaction, participants were asked a series of questions about the frequency of thoughts in relation to  multiple characteristics of their partner [@garcia2016objectification]. Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts. All questions were rated on a scale from 1 (not at all) to 7 (constantly). Objectification was measured by taking the difference between the average frequency of thought about their partner’s external traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intsoo_alpha)[1,1]` for Sample 2) and frequency of thought about their partner’s internal traits ($\alpha$ = `r printnum(clark_extsoo_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_extsoo_alpha)[1,1]` for Sample 2). A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite.

@@

```{r theorfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
include_graphics("theor_figure.jpg")
```

This study sought to detect whether partners’ objectification of one another affected state self-objectification (SSO). Specifically, we were interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction. In addition, we also tested if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification. Further, we investigated the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.

While past studies investigating objectification in interactions used dyadic path analysis [@garcia2016objectification], the current study used multilevel modeling proceedures. Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs), as we have here [@ledermann2017analyzing; @garcia2015moderation]. One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means), but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural]. Further, @olsen2006structural details how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models. The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation patterns. The online supplementary materials contains analysis using SEM. See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.

Testing our hypotheses in the current, same-gender, sample, involves using the Actor-Partner Independence Model (APIM) approach for each outcome variable (i.e., endogenous variable in Figure\ \@ref(fig:theorfigure)). Thus, we ran five APIM's to test all the hypothesized relationships. See Figure\ \@ref(fig:apim) for a basic APIM model. The APIM includes effects due to one's own, as well as one's partner's, predictor variables ($X$'s) on the one's own outcome variable ($Y$). The current study deals with indistinguishable dyads, meaning the designation of who is designated as "actor" and who is designated as "partner" is arbitrary. These analyses are considered exploratory, given the lack of prior research theorizing about these linkages.

@@
